Results

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
preparing submission
figures moved to end of doc
removed cross ref to supplement

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *corrugator* and *levator* activity.
Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).

@@

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```
Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found online on OSF (<https://osf.io/vnj8x/>).

@@

```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block. Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block. The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05. $N=120$. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
```

@@

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, which we have reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$ 
As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *corrugator* and *levator* activity.
Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).

@@

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.

@@

Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found online on OSF (<https://osf.io/vnj8x/>).

@@

@@

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, which we have reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$ 
As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the supplementary material.
